\documentclass[10pt, draftclsnofoot, onecolumn]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage[margin=.75in,footskip=0.25in]{geometry}

\title{Fun with Neural Entanglement \\Problem Statement}
\author{William Wodrich, CS461 Fall 2018}
\date{October 2018}

\begin{document}
\maketitle
\section{Project Abstract}
Neural networks require a large amount of data to train effective neural network inference engines. The purpose of this project is to lessen the amount of data required to train a neural network by making neural networks more effective with a given data set. This will be done by manually modifying the weights of the nodes of the neural network once it has already been trained. The success of this project will be measured by its ability to increase the effectiveness of a neural network on a given data set. Additionally, this project will give its members more knowledge on neural networks in general, training and implementing neural networks, and applications of neural networks.

\section{Problem Definition}
This project is first and foremost a research project focusing on neural networks. When a neural network is created, a large amount of data is required to create an accurate neural network inference engine. The purpose of the research in this project is to train neural networks, then manually modify the weights of the nodes in the neural networks and measure the effect of the engine after modifications. A lot of this project will be experimentation with neural networks and measuring the effectiveness of the neural network inference engines once they are trained. Additionally, this project will include researching possible applications of neural networks, and building neural networks to be combined into global neural network. 

Ideally, the research from neural networks will be fruitful, and a paper, or an idea for a paper will emerge from this project. However, the primary issue this project is attempting to solve is to lessen the amount of data required to create an effective neural network inference engine.

\section{Introduction to Neural Networks}
Artificial Neural Networks is a rising field in computer science. They have been used to solve difficult and large software problems such as image detection and voice to ext technologies. Every large company in Silicon Valley is investing resources into AI, and neural networks are a large component on AI.

Neural networks are structured similar to the biological neural networks that live inside our brains. Similar to our brains learning from experience, neural networks do not initially understand how to preform a task, they have to be trained to do the task through learning from a large data set. For example, voice to text neural networks are trained for each word they are able to translate. Each word trained required a data set of a sound byte of a spoken word along with the correct written interpretation of the word. With enough correlations between the sound of a word and the written word, the neural network inference engine will be able to accurately guess the written word from hearing the sound of the word spoken. Once a neural network has been trained, it can be used as a neural network inference engine, which can infer what a piece of data is based upon its training.

Neural networks are structured such that there are several layers of nodes connected together. Most notably, there is an input layer of nodes, and an output layer of nodes. When a neural network is trained, large amounts of data is inserted into the input layer of the network. When a neural network is used as an inference engine, one sample of data is inserted into the input layer of the neural network, then the result (of inference) is read from the output layer of the neural network. The amount of "hidden" layers in between the input layer and the output layer of the can very, and the number of these layers can influence the effectiveness of the neural network inference engine.

\section{Proposed Solution}

This project seeks to lessen amount of data required to train an effective neural network inference engine. This will be done my making neural networks more effective with a given set of data. Generally, a neural network requires more data to make the neural network inference engine more effective. Hence, by making a neural network more effective, you are essentially building a neural network that requires less data to train to that level of effectiveness.

This project seeks to make neural network inference engines more effective without the requirement of more data through manually and deliberately modifying the weights of the nodes in the neural network. 

Manually modifying the coefficients of the nodes in the neural network does not by any means make a neural network automatically more effective. This means that large amounts of research and trial and error is required for making this solution successful.

\section{Measurement of Project Success}
This project will create and train a neural network. Once this neural network is trained, tests will be preformed on the success rate of the neural network inference engine. The weights of the nodes in the neural network inference engine will be deliberately modified. Then the same tests will be run on the modified neural network inference engine to evaluate its success rate. The success of this project will be measured on its ability to modify a neural network inference engine such that is has a higher success rate when it is tested.

Achieving a higher success rate from a modified neural network inference engine may be difficult, so there will be additional metrics to measure the success of this project. Firstly, it is a large milestone to understand neural networks well enough to build them, so knowledge attained will be a measure of success. This knowledge should cover more than simply how to scaffold and train neural networks. Knowledge should also be gained in applications of neural networks, and how they can be most effectively implemented.

Building an effective neural network inference engine in general will also be a milestone for this project. This in itself will require a lot of knowledge of neural network frameworks, transforming data to an effective format for a neural network, and acquiring enough data to create an effective neural network inference engine.

Creating a more effective neural network inference engine is the ultimate goal of this project. However, attaining the knowledge surrounding neural networks and attaining the experience building and training neural networks will also be a success.

\end{document}
